\sysfull

### 2018-08-05 paper/asplos19/intro.tex

\textbf{Crucial Drawback of Static Task Decomposition.} Task-based programming and execution models require a programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to statically decompose a program into a collection of tasks. A \emph{task}, a top level function, can include arbitrary computation that should be executed despite arbitrarily-timed power failures. The programmer (or a compiler) explicitly expresses task-to-task control flow. Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and shows how tasks transitions can impose a runtime overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at runtime. A programmer may thus create very large tasks in an attempt to reduce task transitions overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk, existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing lead to the following \emph{dilemma}: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete but incur a high task transition and commit overhead?

\textbf{Challenges and Contributions.} This paper introduces \sys: a new task-based system that employs \emph{adaptive task size execution by task coalescing and splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overheads \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks or splits them (see again Fig.~\ref{fig:coalesce}) based on the estimated energy availability without demanding any hardware support. To the best of our knowledge, \sys is the only task-based system that guarantees forward progress for any statically-defined tasks or energy storage sizes.

@@

\item[C1] \emph{Overcoming Task Transition Overhead:} given unpredictable incoming energy, how to save computation progress as rare as possible? \sys tries to minimize task transition overhead by estimating energy conditions at run-time using \emph{recent execution history} as a metric.

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly gives rise to the need for dynamic memory consistency handling. How to dynamically detect inter-task data dependencies and ensure efficient protection against power interrupts? \sys does so by using a novel approach called \emph{dynamic group privatization}---performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys protects global variables in a batch. Moreover, it optimizes data transfers by using Direct Memory Access (DMA).

\item[C3] \emph{Ensuring Task Termination:} a static task decomposition model assumes that each single task can execute to completion. If the hardware energy buffer provides inadequate energy to execute each single task to completion, a program will not terminate~\cite{cleancut_2018}. Under such conditions, how to enable the dynamic execution model to progress on a sub-task level? To avoid non-termination under adverse energy conditions, \sys uses a novel timer-based {\em partial task commit} mechanism \note{should we instead cite Ratchet?}. Partial execution avoids non-termination by committing the intermediate state of a long-running task that has repeatedly failed and restarted.

>>>>

\textbf{Crucial Drawback of Static Task Decomposition.} Task-based programming and execution models require a programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to statically decompose a program into a collection of tasks. A \emph{task}, a top level function, can include arbitrary computation that should be executed despite arbitrarily-timed power failures. The programmer (or a compiler) explicitly expresses task-to-task control flow. Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and shows how tasks transitions can impose a runtime overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at runtime. A programmer may thus create very large tasks in an attempt to reduce task transitions overhead. However, a large task may require more energy to complete than a device's fixed hardware energy buffer can hold, which may lead to a task \emph{non-termination} problem. To eliminate this risk, existing systems require the programmer to decompose a program into small tasks to preserve execution progress. These constraints on task sizing lead to the following \emph{dilemma}: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete but incur a high task transition and commit overhead?

\textbf{Challenges and Contributions.} We introduce \sys: a new task-based system that employs \emph{adaptive task size execution by task coalescing and splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overheads \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks or splits them (see again Fig.~\ref{fig:coalesce}) based on the estimated energy availability without demanding any hardware support. To the best of our knowledge, \sys is the only system that guarantees forward progress for any statically-defined tasks or energy storage sizes.

@@

\item[C1] \emph{Overcoming Task Transition Overhead:} given unpredictable incoming energy, how to save computation progress, i.e. saving state at task transitions, as rare as possible? \sys tries to minimize task transition overhead by estimating energy conditions at run-time using \emph{recent execution history} as a metric.

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly gives rises  the need for dynamic memory consistency handling. This leads to the second challenge: how to dynamically detect inter-task data dependencies and ensure efficient protection against power interrupts? \sys addresses this challenge by using a novel approach called \emph{dynamic group privatization}---performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys protects global variables in a batch. Moreover, it optimizes data transfers by using Direct Memory Access (DMA).

\item[C3] \emph{Ensuring Task Termination:} a static task decomposition model assumes that each task can execute to completion. If the hardware energy buffer provides inadequate energy to execute each task to completion, a program will not terminate~\cite{cleancut_2018}. This leads to a third challenge: how to enable the dynamic execution model to progress on a sub-task level? To avoid non-termination under adverse energy conditions, \sys uses a novel timer-based {\em partial task commit} mechanism, inspired by~\cite{ratchet}. Partial execution avoids non-termination by committing the intermediate state of a long-running task that has repeatedly failed and restarted.
